### 2025-07-14 conteudo/background/refactor.tex
add sowrk 11/05
add paragraph about contrib and remove some todo
add inline method to refactoring

\todo[inline]{Reconsider if I need this function anymore.}

@@

>>>>

@@

\paragraph{Inline Method.}

The inline method involves replacing a function call with the entire body of 
the function, which is copied to where the function is called. One of the 
advantages of this method is reducing the number of unnecessary methods and 
abstraction in the code, making the code more straightforward
\citep{refactorbook}.
